Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-07 paper/paper.tex
Improvement of figure 3 (still need to agree on the reference signal entry location (should be after the ADC) Monor fixes

\maketitle
\begin{abstract}
Modern control systems are by and large implemented via digital microcontrollers, 
which are designed to work in an embedded environment, 
within a dynamical plant that can present physical components. 
%
This poses a new dimension to the problem of controllers synthesis,   
which is classically studied in digital control literature. 
%
In this study, we plan to provide a principled approach to extend this literature in a number of directions: 
we are interested in quantitative tasks;  
we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
and we encompass the compete range of approximations, related to time discretisation, quantisation effects, 
and finite-precision representations (with related rounding errors). To this end, 
we propose a CEGIS-based solution that uses inductive invariant synthesis in conjunction with a digital verification algorithm 
to find a parametric solution for a digital controller given a continuous plant specification. 
\end{abstract}

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC).  
\red{[do we really need to regard the quantisation effects of the ZOH in the DAC? Elaborate next:]}
$G(s)$ is the continuous-time model of the plant, from
which output samples are taken and quantized ($Q1$) by means of an
analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
($Q1$ and $Q2$) will present some contribution for the total quantization
noise.
%
\begin{figure}[ht]
\centering
\resizebox{.5\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \node[draw=none] (r) {r};
%   \& \coordinate (aux0);
   \& \node[circle] (circle) {};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {{\sc Q1}};} 
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1cm,
	label=\textbf{DAC},] (dac) {};
     \node[fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {{\sc Q2}};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \& \coordinate (aux1);
   \& \node[draw=none] (y) {y};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (y);
  \path  
   (circle.east) edge (switch1)
   (switch2) edge (q1.west)
   (q1.east) edge (cz.west)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (gs.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
\end{figure}

@@

First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal. But we handle the noise deterministically. How so? Where is the catch? ]}
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) \red{[do we need the second? See my further comments below.]} \green{There was a typo in \eqref{eq:deltaG_final}. It was missing $q_{1}$ and $q_{1}$, both effects are considered here. } \red{[why are both needed? I'm still unconvinced.]}
are white noises.
%
\end{myassumption}

@@

\begin{myassumption}
%
The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows) may be disregard. %\red{[explain difference btw overflows and saturations. Also, do we care about limit cycles? I'd quite happily disregard them.]}
%
\end{myassumption}

>>>>

\maketitle
\begin{abstract}
Modern control systems are by and large implemented via digital microcontrollers, 
which are designed to work in an embedded environment, 
within a dynamical plant that can present physical components. 
%
This poses a new dimension to the problem of controllers synthesis,   
which is classically studied in digital control literature. 
%
In this study, we plan to provide a principled approach to extend this literature in a number of directions: 
we are interested in quantitative tasks;  
we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
and we encompass the complete range of approximations, related to time discretisation, quantisation effects, 
and finite-precision representations (with related rounding errors). To this end, 
we propose a CEGIS-based solution that uses inductive invariant synthesis in conjunction with a digital verification algorithm 
to find a parametric solution for a digital controller given a continuous plant specification. 
\end{abstract}

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC). The quantization occurs because the DAC resolution may be different from the fixed point representation of the controller.  
$G(s)$ is the continuous-time model of the plant, from
which output samples are taken and quantized ($Q1$) by means of an
analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
($Q1$ and $Q2$) will present some contribution for the total quantization
noise.
%    
\begin{figure}[ht]
\centering

\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

\resizebox{.5\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \node[draw=none] (r) {r};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (u) at ([xshift=1cm,yshift=.1cm]cz)  {u};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \& \coordinate (aux1);
   \& \node[draw=none] (y) {y};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (y);
  \path  
   (circle.east) edge (switch1)
   (switch2) edge (q1.west)
   (q1.east) edge (cz.west)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (gs.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
\end{figure}

@@

First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal. But we handle the noise deterministically. How so? Where is the catch? ]}
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are white noises.
%
\end{myassumption}

@@

\begin{myassumption}
%
The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows, ADC/DAC nonlinearities) will be disregarded.
\red{should we explicitly state we want a controller that does not saturate?}
%
\end{myassumption}
